---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# eurostat R package 3.7.5 fork: sans sf edition (3.7.5.9000)

R tools to access open data from [Eurostat](https://ec.europa.eu/eurostat). Data search, download, manipulation and visualization. 

This fork follows the main [rOpenGov repository](https://github.com/rOpenGov/eurostat) with one crucial difference: **dependency and functionalities related to sf package have been removed**. This is to increase the package's usefulness in systems where installing the sf package could cause issues.

This fork uses version number x.x.x.9000 to differentiate it from the main branch version.

### Installation and use

```{r, eval = FALSE}
# Install from GitHub
library(devtools)
devtools::install_github("pitkant/eurostat")
```

The package provides several different ways to get datasets from Eurostat. Searching for data is one way, if you know what to look for.

```{r example, eval = TRUE}
# Load the package
library(eurostat)

# Perform a simple search and print a table
passengers <- search_eurostat("passenger transport")
knitr::kable(head(passengers))
```

See the [Tutorial](https://ropengov.github.io/eurostat/articles/website/eurostat_tutorial.html) and other resources at the [package homepage](https://ropengov.github.io/eurostat/) for more information and examples.

### Recommended packages

It is recommended to install the `giscoR` package (https://dieghernan.github.io/giscoR/). This is another API package that provides R tools for Eurostat geographic data to support geospatial analysis and visualization.

### Contribute

Please make contributions, open issues and pull requests in the main branch: [https://github.com/ropengov/eurostat/](https://github.com/ropengov/eurostat/)

### Acknowledgements

**Kindly cite this work** as follows: [Leo Lahti](https://github.com/antagomir), Przemyslaw Biecek, Markus Kainu and Janne Huovari. Retrieval and analysis of Eurostat open data with the eurostat package. [R Journal 9(1):385-392, 2017](https://journal.r-project.org/archive/2017/RJ-2017-019/index.html). R package version `r sessionInfo()$otherPkgs$eurostat$Version`. URL: [https://ropengov.github.io/eurostat/](https://ropengov.github.io/eurostat/)

We are grateful to all [contributors](https://github.com/ropengov/eurostat/graphs/contributors), including Daniel Antal, Joona Lehtomäki, Francois Briatte, and Oliver Reiter, and for the [Eurostat](https://ec.europa.eu/eurostat/) open data portal! This project is part of [rOpenGov](http://ropengov.org).


### Disclaimer

This package is in no way officially related to or endorsed by Eurostat.